A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex

\begin{figure}[htbp]
\includegraphics[width=\columnwidth]{ast_sizes}
\caption{Input sizes} \label{fig:ast-size}
\end{figure}

@@

One of the main differences of the R \eval with the javascript one is how it
interacts with \emph{scope}, or environments in R. In Javascript, \c{eval}
can access the local scope and the global scope. In R, \c{eval} has an
argument \c{envir} to indicate in which environment its first argument,
after being resolved, must be evaluated. By default, it is equal to \c{parent.frame()}, which is the parent environment of the \c{eval} call.

@@

We classify the environment from two points of view:
\begin{itemize}
	\item the \emph{default} assignment environment \c{eval} writes new bindings.\footnote{It is the default one but the expression in \eval can always write in any other environments using \c{assign} or in the parent environment using \c{<<-}.}
	\item in which \emph{existing} environment \c{eval} reads. It is the first non new environment. \c{eval} will also be able to read in all parent environment of that environment. 
\end{itemize}

% Variability: how many different envir class, and different envir expr, for one call site?

@@

\begin{figure}[!h]
    \includegraphics[width=\columnwidth]{polymorphism}
    \caption{Degree of polymorphism of \c{expr} per call sites.} \label{fig:polymorphism}
\end{figure}

>>>>

\begin{figure}[htbp]
	\centering
\includegraphics[width=\columnwidth]{ast_sizes}
\caption{Input sizes} \label{fig:ast-size}
\end{figure}

@@

One of the main differences of the R \eval with the javascript one is how it
interacts with \emph{scope}, or environments in R. In Javascript, \c{eval}
can access the local scope and the global scope. In R, \c{eval} has an
argument \c{envir} to indicate in which environment its first argument,
after being resolved, must be evaluated. By default, it is equal to \c{parent.frame()}, which is the parent environment of the \c{eval} call. This default argument happens in \miss{XX\%} of the eval calls.

@@

There are two main environments affected by \eval:
\begin{itemize}
	\item the \emph{existing} environment where \c{eval} reads. It is the first non new environment. \c{eval} will also be able to read in all parent environment of that environment. It can be the global environment, a package environment, an empty environment, the callee environment, or a parent environment of the callee.
	\item the \emph{default} assignment environment \c{eval} writes new bindings.\footnote{It is the default one but the expression in \eval can always write in any other environments using \c{assign} or in the parent environment using \c{<<-}.} If it is different from the read environment and is a new one that inherits from the read environment, we add a symbol \texttt{+} after the read environment.
\end{itemize}

As shown in Figure~\ref{fig:environments}, \eval in R is often performed in the global environment.  It is also used a lot to evaluate in the context of a dataframe (\emph{list} environment).

% Variability: how many different envir class, and different envir expr, for one call site?
\begin{figure*}[htbp]
	\centering
	\includegraphics[width=\linewidth]{environments.pdf}
	\caption{The environments in which the expression is evaluated. \c{NA} corresponds to the default environment.} \label{fig:environments}
\end{figure*}

@@

\begin{figure}[!h]
	\centering
    \includegraphics[width=\columnwidth]{polymorphism}
    \caption{Degree of polymorphism of \c{expr} per call sites.} \label{fig:polymorphism}
\end{figure}
